What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-14 android-stacks.tex

Techniques for error detection and handling are not  an optional add-on but a
fundamental part of the system~\cite{bruntink2006discovering}. Several
approaches exists for detecting errors and responding to them, such as the return-code 
idiom (very popular in C programs and operating systems), and the exception handling 
mechanism, embedded in many main stream programming languages.

@@

In this section, we present works that are related to our own, distributed in
three categories: i) works that use the information available on stack traces;
ii) empirical studies on the usage of Java exceptions and its fault proneness;
and iii) tools to extract stack traces information from natural language artifacts
(i.e., issues and emails).
%, and iv) empirical studies involving Android apps.

@@

@@

In this work we present an exploratory study on which we mined the stack 
traces embedded in all issues of Java projects available GitHub, and analyzed in mode detail thr
stack traces reported on a subset of 482 Android projects. In this study, the information extracted 
from stack traces was used in combination with source code and bytecode analysis to 
pin-point patterns of exceptions (mis-)use in Java. And some patterns of exception
(mis)-use were consistently detected such as: unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that Java hybrid exception
model is not fully used according to its purpose; undocumented runtime
exceptions signaled by third party code (which makes almost impossible for
library clients to protect against such exceptions); and a high prevalence of
java.lang exceptions reported on issues (representing approximately 50\% of the
analyzed issues). Such (mis)uses detected in out study can negatively affect the 
robustness of current Java software systems. Such results shed light to needs for  
 developing tools support to help developers dealing with such problems and 
improving the design of exception handling mechanism in Java.

>>>>

Techniques for error detection and handling are not  an optional add-on but a
fundamental part of any system~\cite{bruntink2006discovering}. Several
approaches exist for detecting errors and responding to them, such as the return-code 
idiom (widely used in systems written in C), and the exception handling 
mechanism, embedded in many main-stream programming languages.

@@

In this section, we present work that is related to the present paper, divided into
three categories: i) papers that use the information available on stack traces;
ii) empirical studies on the usage of Java exceptions and its fault proneness;
and iii) tools to extract stack traces information from natural language artifacts
(e.g., issues and emails).
%, and iv) empirical studies involving Android apps.

@@

\enlargethispage{-2\baselineskip}

@@

In this paper we present an exploratory study in which we mined the stack 
traces embedded in all issues of Java projects available GitHub.
Furthermore, we analyzed in more detail the
stack traces reported on a subset of 482 Android projects. In this study, the information extracted 
from stack traces was used in combination with source code and bytecode analysis to 
pin-point patterns of exception use and misuse in Java.
Certain patterns of exception
(mis)-use were consistently detected such as unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that  the Java hybrid exception
model is not fully used according to its purpose; undocumented runtime
exceptions signaled by third party code (which makes it almost impossible for
library clients to protect against such exceptions); 
and a high prevalence of
\texttt{java.lang} exceptions reported on issues (representing approximately 50\% of the
analyzed issues). Such (mis)uses detected in our study can negatively affect the 
robustness of current Java software systems. Our results call for  
 developing tools support to help developers dealing with such problems and 
improving the design of the exception handling mechanism in Java.
